Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-15 Ben_Manuscripts/transport/Outline.tex
added comments to outline.
Updates

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

@@

@@

  	\item Can we describe the transport mechanisms using pre-existing 
  	mathematical models. \label{question:math}

  	A mathematical model may provide additional insight into the transport
  	mechanisms and, in future work, can help relate performance on the 
  	timescales studied with MD to macroscopic timescales. We will use
  	qualitative and semi-quantitative arguments in order to choose a 
  	governing model.

@@

  Python scripts used to set up systems and conduct post-simulation trajectory analysis are
  available online at \texttt{https://github.com/bencoscia/llcsim}.

@@

  \subsection*{System Setup}

@@

  %BJC: reference to supporting info with more details on water partition
  %BJC: or should that go in the main body results?
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is about 2:1 water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See supporting info for water equilibration simulation data.
	\item We iteratively adjusted the pore radius in our systems until the right amount of water
	fit in the pores when we ran \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  \noindent We added 6 solute molecules to each pore of the equilibrated cross-linked
  configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimization.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data over the course of 1 $\mu$s MD simulations
  \end{itemize}

  \subsection*{Solute Parameterization}

@@

  \noindent We measured the time-averaged $z$-direction mean squared 
  displacement (MSD) of the centers of mass of each solute over the 
  course of 1 $\mu$s MD simulations using Equation~\ref{eqn:tamsd}.
  \begin{itemize}
    \item \begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\label{eqn:tamsd}
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
	\item Generally, the MSD grows according to Equation~\ref{eqn:msd_form},
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	\item where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
	motion respectively.
	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
	MSD given by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
	\item The ensemble MSD is calculated with respect to a reference position and
	hence carries some dependence on its starting point.
	\item The time-averaged MSD averages over all possible time lags of a given 
	length, effectively eliminating any initial configuration dependence and generating
	an increased number of observations. 
	\item For ergodic systems, both types of MSDs will be equal.
	\item Since we have a small number of solutes with which to generate statistics
	and because we are not calculating values for $\alpha$ in this particular study,
	we will only use the time-averaged MSD.
  \end{itemize}

@@

@@

@@

  \subsection*{Radial Density Functions}

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
	\item We obtain the best RDF by constructing splines that run through the
	pore centers.
	\item We construct the splines by dividing the membrane into 10 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the linearly
	interpolated ($x$, $y$)	coordinates of the pore center calculated based
	on the spline.
  \end{itemize}

  \subsection*{Identification of Hydrogen Bonds}

  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

  \subsection*{Coordination number}

  We quantified the coordination of solutes with surrounding molecules.
  \begin{itemize}
  	\item For each frame, we counted the identities and number of
  	coordinated molecules to a given solute based on a distance cut-off. 
	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

  Using four different methods, Rowley and Roux observed peaks in the radial
  distribution function for sodium coordinated with water at an O-Na distance 
  of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. We used 2.5 \AA~as
  the distance cutoff.  % BJC: this might be too strict. I've seen literature where they define 3.2 angstroms as the cutoff

@@

  \subsection*{Structure and Transport of Membrane Constituents}\label{section:membrane_components}

  %BJC: Probably do analysis on pure water system for this section.

@@

  %BJC: I'm not sure if would be better to normalize the densities so that the
  % shape of the sodium density is more pronounced
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  The 5 wt \% system (a) appears to be much more crowded by monomers than the 
  10 wt \% system (b). Head groups in (a) are densest closer to the pore center than
  in (b). A small amount of tail components find their way close to the pore center 
  of the 5 wt \% system. }\label{fig:component_densities}
  \end{figure}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item In bulk water, it is estimated that sodium coordinates with 5.6 - 5.8 water
    molecules~\cite{rowley_solvation_2012}
    \item In our system, on average, each sodium ion is coordinated to about 1.7 
    water molecules in the 10 wt \% system and 1.15 water molecules in the 5 wt\% 
    system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}
    \item On average, sodium ions coordinate with 0.5 head group oxygen atoms in the
    10 wt \% water system and 0.4 head group oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

  % BJC: This figure is from methanol simulations. Will be replaced by pure water
  % simulations
  % BJC: I can probably just report the averages rather than plot this
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
  \caption{}\label{fig:na_water_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
  \end{subfigure}
  \end{figure}

@@

  \noindent The MSDs are not a monotonic function of solute size.
  \begin{itemize}
  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
  	\item There are numerous examples of solutes in our study that do not 
  	follow the behavior set forth by the Stokes-Einstein equation which 
  	implies that solute MSD should be inversely related to solute size.  % citation
  	\item This behavior is not entirely surprising but worth emphasizing. 
  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
  	the solute radius is much larger than the solvent, should break down once
  	solute and solvent are of comparable size.
  	\item Membranes, including that studied here, are often characterized 
  	with size-exclusion experiments which emphasizes selectivity based on the ability
  	to enter a given pore. 
  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
  	becomes of secondary importance since the primary purpose of these membranes is to 
  	separate molecules whose sizes are on the same order as water.
  	\item In order to handle complex waste streams with molecules of similar size,
  	it is important to take advantage of material properties other than pore size. 
%  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
%  	than half of all solutes studied. 
%  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
%  	\item Transport is clearly affected by factors other than molecular size. 
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC: missing a few since those simulations just got started
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d).}\label{fig:msds}
  \end{figure}

  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and the hops occur when solutes are close to the pore center. (b) The
  time-averaged MSD of ethanol is not linear which suggests transport is governed 
  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
  \end{figure}

  %BJC: need to check whether sodium ion association is exhibited by all solutes
  In addition to solute trapping in dense monomer regions, we observe a second
  trapping mechanism caused by preferential hydrogen bonding between 
  hydrogen bond donor solutes and monomer carboxylate groups. 
  \begin{itemize}
    \item Of the time spent donating hydrogen atom(s), x \% of the hydrogen
    bonds occur between solutes and carboxylate groups as opposed to solutes
    with water. 
    \item This shows a high preference for the carboxylate anions since there
    are 5 times more water molecules in the system.
    \item The carboxylate oxygen atoms have a slightly higher partial negative
    charge than water molecules.
    \item Additionally, on average, each sodium ion is coordinated to 1.7 water
    molecules. Roughly all of the water in the pore region is usually coordinated
    to a sodium ion which decreases their availability to solutes.
  \end{itemize}

  Finally, we see instances of solutes which become immobilized or slowed by 
  association with sodium counterions. 
  \begin{itemize}
    \item Much like water, the polarity of the solutes leaves partial negative
    charges which are stabilized through electrostatic interactions with sodium ions.
    \item There are many cases in which polar groups bind to sodium ions for at
    least a few time steps. 
    \item There are some cases where solutes become immobilized for long periods
    of time while in close proximity to a sodium ion.
    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
    within 2.5 \AA of a sodium ion for the entire length of a trapping occurence.
  \end{itemize}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}

\externaldocument[S-]{Supporting_Information}

@@

  %BJC1: copied from discussion. Need to work this in the right place
  \begin{itemize}  
  	\item Membranes, including that studied here, are often characterized 
  	with size-exclusion experiments which emphasizes selectivity based on the ability
  	to enter a given pore. 
  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
  	becomes of secondary importance since the primary purpose of these membranes is to 
  	separate molecules whose sizes are on the same order as water.
  	\item In order to handle complex waste streams with molecules of similar size,
  	it is important to take advantage of material properties other than pore size. 
  \end{itemize}

@@

%  	\item Can we describe the transport mechanisms using pre-existing 
%  	mathematical models. \label{question:math}
%  	
%  	A mathematical model may provide additional insight into the transport
%  	mechanisms and, in future work, can help relate performance on the 
%  	timescales studied with MD to macroscopic timescales. We will use
%  	qualitative and semi-quantitative arguments in order to choose a 
%  	governing model.

@@

  Python scripts used to set up systems and conduct post-simulation trajectory 
  analysis are available online at \texttt{https://github.com/shirtsgroup/LLC\_Membranes}.
  The appropriate script to use for each of the following calculations is summarized
  in Table~\ref{S-table:python_scripts} of the SI.

@@

  \subsection*{System Setup}\label{method:system_setup}

@@

  %BJC: reference to supporting info with more details on water partition
  %BJC: or should that go in the main body results?
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is a 2:1 ratio of water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See section~\ref{S-section:water_content_equil} of the SI for further details on 
	water equilibration in this system.
	\item We iteratively adjusted the pore radius in our systems until the right amount of water
	fit in the pores when we ran \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  \noindent To study a given solute, we added 6 solute molecules to each pore of the
  equilibrated cross-linked configuration.
  \begin{itemize}
	\item We equally spaced each solute in the pore
	\item 6 solutes per pore provided a balance of a useful amount of data
	for generating statistics and a low degree of interaction between solutes (reference
	to supporting information to show low degree of interaction)
	\item At each insertion point we placed a randomly oriented solute molecule
	then ran a short energy minimization.
	\item We allowed the solutes to equilibrate for 5 ns using berendsen 
	pressure control
	\item We collected transport data over the course of 1 $\mu$s MD simulations
  \end{itemize}

  \subsection*{Solute Parameterization}\label{method:parameterization}

@@

  \noindent We measured the time-averaged $z$-direction mean squared 
  displacement (MSD) of the centers of mass of each solute over the 
  course of 1 $\mu$s MD simulations using Equation~\ref{eqn:tamsd}.
  \begin{itemize}
    \item \begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\label{eqn:tamsd}
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
	\item Generally, the MSD grows according to Equation~\ref{eqn:msd_form},
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	\item where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
	motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
	MSD given by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
	\item The ensemble MSD is calculated with respect to a reference position and
	hence carries some dependence on its starting point.
	\item The time-averaged MSD averages over all possible time lags of a given 
	length, effectively eliminating any initial configuration dependence and generating
	an increased number of observations. 
	\item For ergodic systems, both types of MSDs will be equal.
	\item Since we have a small number of solutes with which to generate statistics
	and because we are not calculating values for $\alpha$ in this particular study,
	we will only use the time-averaged MSD.
  \end{itemize}

@@

  \subsection*{Molecular Size Determination}\label{method:molecular_size}

  In order to determine an effective radius for each solute, we measured the 
  maximum pairwise distance between atoms of each solute over the course of
  a 2.5 ns simulation of solutes dissolved in a cubic box of water.
  \begin{itemize}
    \item Each box consisted of about 2100 water molecules and 6 solutes.
    \item Although there exist more involved methods for determining the 
    hydrodynamic radius~\cite{schultz_determination_1961}, we chose to use
    a simpler and more intuitive metric since we are only interested in
    observing trends in the solute mean squared displacement as a function
    of solute size. 
  \end{itemize}

@@

  %MRS1: we probably only want enough do identify mechanism not to fit anything.  Think about minimum needed for physical understanding.
  %BJC1: right, the following is the bear minimum if we want to mention dwell time and hop lengths at all. Otherwise this can be omitted.

@@

  \subsection*{Radial Density Functions}\label{method:rdfs}
  % BJC1: Should it be Radial Distribution Functions?

  We measured the average radial distance of each solute of interest from the pore
  centers.
  \begin{itemize}
	\item We binned the radial distances and then normalized by the volume
	of the annulus defined by the bin edges.
	\item Although the pores are often described as straight, they have a
	small degree of tortuosity which disrupts the RDF calcuation 
    % MRS1: can you report numerically the tortuosity?
	\item We tried to mitigate the effects of tortuosity by calculating the RDF
	with respect to splines that run through the pore centers.
	\item We construct the splines by dividing the membrane into 10 slices
	in the $z$-direction. Within each slice, we calculate the location of 
	the pore centers based on the average location of the aromatic rings
	that make up the monomer head groups.
	\item When calculating the RDF, the radial distance from the pore center
	is based on the distance between the solute center-of-mass and the linearly
	interpolated ($x$, $y$)	coordinates of the pore center calculated based
	on the spline.
  \end{itemize}

  \subsection*{Identification of Hydrogen Bonds}\label{method:hbonds}

  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
  %we are not picking and choosing results (either consciously or unconsciously) 
  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    \item We tested the sensitivity of our conclusions to this definition in 
    the Supporting Information.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

  \subsection*{Coordination number}\label{method:coordination}

  We quantified the coordination of solute constituent atoms with sodium ions.
  \begin{itemize}
  	\item For each frame, we counted the number of coordinated molecules to a
  	given solute atom based on a distance cut-off. 
  	\item Using four different methods, Rowley and Roux observed peaks in the
  	radial distribution function for sodium coordinated with water at an O-Na
  	distance of between 2.3 and 2.5 \AA~\cite{rowley_solvation_2012}. 
  	\item We used 2.5 \AA~as the distance cutoff.
  	\item We found that this approach is more useful than calculating the
	3D spherical radial distribution function because it gives detailed
	frame-by-frame information rather than an average. 
  \end{itemize}

  Using our procedure we found that sodium ions in a solution of tip3p water
  coordinate with an average of 3.4 water molecules.
  \begin{itemize}
    \item We created a 4 x 4 x 4 nm cubic box of water with the GROMACS tool,
    \texttt{gmx solvate}
    \item We used \texttt{gmx genion} to replace water molecules with sodium
    and chloride ions in order to create a 0.6 M NaCl solution.
    \item We let the system simulate for 5 ns and reported the average
    number of coordinated water molecules per frame after discarding the first ns of 
    simulation. % need to actually do this
    \item We found that the reported average value is not sensitive to NaCl
    concentration (See Supporting Information)
  \end{itemize}

@@

  \subsection*{Structure of Membrane Constituents}\label{section:membrane_components}

  %BJC: Do analysis on pure water system for this section.

@@

  %BJC: I'm not sure if would be better to normalize the densities so that the
  % shape of the sodium density is more pronounced
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS1: explicitly state the normalization used for the RDF.
  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  The 5 wt \% system (a) appears to be much more crowded by monomers than the 
  10 wt \% system (b). Head groups in (a) are densest closer to the pore center than
  in (b). A small amount of tail components find their way close to the pore center 
  of the 5 wt \% system. }\label{fig:component_densities}
  \end{figure}

  We observed transport of sodium, water and 20 other small polar solutes inside the
  membrane nanopores. 
  \begin{itemize}
  	\item First, we will comment on transport of the membrane constituents, water and sodium,
  	in a system absent of any additional solutes.
%    \item There are significantly more water molecules and sodium ions in the membrane
%    than solutes.
    \item Then we will present the general trends that we observe among the set of 
    solutes studied.
  \end{itemize}

  \subsubsection*{Water and Sodium Ions}\label{section:transport_water_sodium}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item In our system, on average, each sodium ion is coordinated to about 1.7 
    water molecules in the 10 wt \% system and 1.15 water molecules in the 5 wt\% 
    system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}
    %MRS1: are ``head group oxygen'' atoms the same as carboxylate? Not clear. 
    \item On average, sodium ions coordinate with 0.5 head group oxygen atoms in the
    10 wt \% water system and 0.4 head group oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

  % BJC: This figure is from methanol simulations. Will be replaced by pure water
  % simulations
  % BJC: I can probably just report the averages rather than plot this
  %MRS1: yeah, this is not really worth a graphic.
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_water_coordination.pdf}
  \caption{}\label{fig:na_water_coordination}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{Na_hg_coordination.pdf}
  \caption{}\label{fig:na_hg_coordination}  % No caption since this probably won't be a figure
  \end{subfigure}
  \end{figure}

  \subsubsection*{Transport of Small Polar Solutes}\label{section:general_transport_solutes}

@@

  \noindent The MSDs are not a monotonic function of solute size.
  \begin{itemize}
  	\item We plotted the solute size against their MSDs in Figure~\ref{fig:msd_radius_5wt} and~\ref{fig:msd_radius_10wt}.
  	\item There are numerous examples of solutes in our study that do not 
  	follow the behavior set forth by the Stokes-Einstein equation which 
  	implies that solute MSD should be inversely related to solute size.  % citation
        %MRS1: can you plot on the figure what the relatioship SHOULD look like?  It sort of looks linear-ish (especially 5).
  	\item This behavior is not entirely surprising but worth emphasizing. 
  	\item It is expected that the Stokes-Einstein relationship, which assumes that 
  	the solute radius is much larger than the solvent, should break down once
  	solute and solvent are of comparable size.
        %MRS1: these points below seem more like intro points.

  	\item Membranes, including that studied here, are often characterized 
  	with size-exclusion experiments which emphasizes selectivity based on the ability
  	to enter a given pore. 
  	\item Once we reach the nm to sub-nm pore size regime, size-exclusion 
  	becomes of secondary importance since the primary purpose of these membranes is to 
  	separate molecules whose sizes are on the same order as water.
  	\item In order to handle complex waste streams with molecules of similar size,
  	it is important to take advantage of material properties other than pore size. 
%  	\item Tetrose, our fifth largest solute, has an average MSD higher than more 
%  	than half of all solutes studied. 
%  	\item The two slowest solutes, DMF and THF, are smaller than 10 faster solutes.
%  	\item Transport is clearly affected by factors other than molecular size. 
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC: missing a few since those simulations just got started
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d).}\label{fig:msds}
  \end{figure}  
  %MRS1: Having so much data here grapically is nice.  ought to think how else data can be displayed. Perhaps figures with the dwell times as well?  Depends on if those are being shown.  2D scatter plots with average partitioning distance of solute vs. MSD? We should keep brainstorming which will be most relevant. 
  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{colorful_example_ztraces.pdf}
  \caption{}\label{fig:example_ztraces}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\linewidth]{example_msd.pdf}
  \caption{}\label{fig:example_msd}
  \end{subfigure}
  %MRS1: nice graph!
  \caption{All solutes show subdiffusive transport behavior inside the membrane's
  nanopores, similar to that exhibited by ethanol. (a) The $z$-coordinate trace of
  3 representative ethanol COMs shows clear periods of entrapment separated by hops.
  In general, the longest dwell times occur when solutes are situated far from the
  pore center and the hops occur when solutes are close to the pore center. (b) The
  time-averaged MSD of ethanol is not linear which suggests transport is governed 
  by an anomalous subdiffusion process.}\label{fig:qualitative_mechanisms}
  \end{figure}

  %BJC: need to check whether sodium ion association is exhibited by all solutes
  In addition to solute trapping in dense monomer regions, we observe a second
  trapping mechanism caused by preferential hydrogen bonding between 
  hydrogen bond donor solutes and monomer carboxylate groups. 
  %MRS1: is there a way we can deconvolute these two-three mechanisms?
  \begin{itemize}
    \item Of the time spent donating hydrogen atom(s), x \% of the hydrogen
    bonds occur between solutes and carboxylate groups as opposed to solutes
    with water. 
    \item This shows a high preference for the carboxylate anions since there
    are 5 times more water molecules in the system.
    %MRS1: carboxylate also has net negative charge - not just higher negative partial charge,
    %also no extra neutralizing positive partial charge nearby.
    \item The carboxylate oxygen atoms have a slightly higher partial negative
    charge than water molecules.
    \item Additionally, on average, each sodium ion is coordinated to 1.7 water
    molecules. Roughly all of the water in the pore region is usually coordinated
    to a sodium ion which decreases their availability to solutes.
    %MRS1: this should lead to reduced ability to solvate positive things, but shouldn't reduce H-boonding that much?
  \end{itemize}

  Finally, we see instances of solutes which become immobilized or slowed by 
  association with sodium counterions. 
  \begin{itemize}
    \item Much like water, the polarity of the solutes leaves partial negative
    charges which are stabilized through electrostatic interactions with sodium ions.
    \item There are many cases in which polar groups bind to sodium ions for at
    %MRS1: a 'few times steps' seems irrelevant.   
    least a few time steps. 
    \item There are some cases where solutes become immobilized for long periods
    of time while in close proximity to a sodium ion.
    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
    within 2.5 \AA of a sodium ion for the entire length of a trapping occurence.
  \end{itemize}
